Group 9 Presentation

### 2021-12-08 presentation.Rmd
Removed warnings from lasso and KNN, so they do not show in the presentation.html

+ ST_Slope:

@@

@@

@@

# MSE values to use:
best_lambda_lasso
lasso_MSE
num_zeros

@@

#Confusion Matrix
predict_bag <- predict(bagging, newdata = test)
predicted_bag <- ifelse(predict_bag>0.5,1,0)
confm_bag<-table(predict_bag,test$HeartDisease,)

@@

- Tuning Parmeters Choosen= 600 trees, shrinkage=0.01, interaction= 2.

@@

confboost<-table(predicted = boostpred, actual = test$HeartDisease)
confboost
error<-(confboost[1,1]+confboost[2,2])/sum(confboost)
overall_boost <- error
```

@@

paste("the overall fraction of correct predictions in the test dataset is :", acc)
```

>>>>

+ ST_Slope during exercise:

@@

```{r message=FALSE, warning=FALSE,echo=FALSE}

@@

```{r message=FALSE, warning=FALSE}

@@

# MSE values to use:
paste("Tuning Lambda",best_lambda_lasso)
#lasso_MSE
paste("Number of zeros",num_zeros)

@@

#Confusion Matrix
predict_bag <- predict(bagging, newdata = test)
predicted_bag <- ifelse(predict_bag>0.5,1,0)
confm_bag<-table(predicted_bag,test$HeartDisease)

@@

- Tuning Parameters: n= 600 trees, shrinkage=0.01, interaction= 2.

@@

confboost<-table(predicted = boostpred, actual = test$HeartDisease)
confboost
error<-(confboost[1,1]+confboost[2,2])/sum(confboost)
overall_boost <- error
overall_boost
```

@@

paste("The overall fraction of correct predictions in the test dataset is :", acc)
```
